\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-08 doc/paper.tex
spell check.

Nonetheless \fs provides help for such cases in several ways. One may
adjust initial guesses specified in the FlexibleSUSY modle file, such
as changing the choice of HighScaleFirstGuess or altering
HighScaleMinimum and HighScaleMaximum which can be used to push the
iteration back towards where the solution should be if it gets off
track.

For experienced users the clear code structure also allows the
possibility of direct adaption of the code.  For example in the case
of the E6SSM we observed that for some points the presence of new
Yuwawas had a big impact on the RGEs for the VEVS.  When the user
chooses to set these Yukawas at the GUT scale, then on the initial run
up to the GUT scale they will be set to zero.  As a result the VEV
RGEs on the run up are quite different to the VEV RGEs on the run down
so that the VEVs used at the SUSY scale are far from the correct
values and this can create an instability leading eventually to
non-perturbative in the couplings.  This can be fixed by adapting the
algorithm so that thge VEVs are stored at the SUSY scale.  However a
simpler, if less clean, fix is to directly modify the generated code
by adding three lines to the file
\code{<model>_two_scale_susy_parameters.cpp} just before the beta
functions are returned in method
\code{<model>_susy_parameters::calc_beta()}.

@@

Finally instead of tinkering with the two-scale solver one may wish to replace it entirely. the modular design of FlexibleSUSY allows for the solver
for the boundary value problem to be replaced. An alternative solver
with better convergence properties (at the expense of slower speed) is
already planned for a later release.

>>>>

Nonetheless \fs provides help for such cases in several ways. One may
adjust initial guesses specified in the FlexibleSUSY model file, such
as changing the choice of \code{HighScaleFirstGuess} or altering
\code{HighScaleMinimum} and \code{HighScaleMaximum} which can be used
to push the iteration back towards where the solution should be if it
gets off track.

For experienced users the clear code structure also allows the
possibility of direct adaption of the code.  For example in the case
of the E6SSM we observed that for some points the presence of new
Yukawas had a big impact on the RGEs for the VEVs.  When the user
chooses to set these Yukawas at the GUT scale, then on the initial run
up to the GUT scale they will be set to zero.  As a result the VEV
RGEs on the run up are quite different to the VEV RGEs on the run down
so that the VEVs used at the SUSY scale are far from the correct
values and this can create an instability leading eventually to
non-perturbative in the couplings.  This can be fixed by adapting the
algorithm so that the VEVs are stored at the SUSY scale.  However a
simpler, if less clean, fix is to directly modify the generated code
by adding three lines to the file
\code{<model>_two_scale_susy_parameters.cpp} just before the beta
functions are returned in method
\code{<model>_susy_parameters::calc_beta()}.

@@

Finally instead of tinkering with the two-scale solver one may wish to
replace it entirely. The modular design of FlexibleSUSY allows for the
solver for the boundary value problem to be replaced. An alternative
solver with better convergence properties (at the expense of slower
speed) is already planned for a later release.
